More Tests

### 2021-11-05 data-raw/informal-tests/informal-tests.Rmd
update tests
update informal tests, and documentation

```{r}
cow_leaderyears <- create_leaderyears(standardize_cow = TRUE)
gw_leaderyears <- create_leaderyears(standardize_cow = FALSE)

@@

```{r}
test_that("Dyad-year additions do not create duplicates", {
  expect_equal(nrow(cow_ddy), nrow(cow_ddy %>% add_cow_trade()))
})
```

>>>>

```{r}
cow_leaderyears <- create_leaderyears(standardize = "cow")
gw_leaderyears <- create_leaderyears(standardize = "gw")

@@

```{r}
test_that("Dyad-year additions do not create duplicates", {
  expect_equal(nrow(cow_ddy), nrow(cow_ddy %>% add_cow_trade()))
  expect_equal(nrow(cow_ddy), nrow(cow_ddy %>% add_fpsim()))
})
```
